%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------
\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}
%------------------------------------------------

\cventry
{Retail Business Services at Ahold Delhaize} % Organization
{Emerging Technology Intern} % Job title
{January 2019 - Present} % Date(s)
{Mooresville, North Carolina} % Location
{ % Description(s) of tasks/responsibilities
\vspace{0.5mm}
\begin{cvitems}
\item {Researched, architected, and implemented a combination of new and existing technologies for an end-to-end frictionless experience for the user in next-gen grocery stores.}
\item {Lead exploratory work in automating Bluetooth connections using software.}
\item {Implemented computer vision for facial recognition and integrated with hardware.}
\item {Maintained vendor relations to correlate business value and development process.}
\item {Collaborated with teams in different disciplines on various projects.}
\item {Worked in an Agile environment and attended daily stand-ups, sprint retrospectives, and backlog refinement meetings.}
\item {Tracked project issues using Jira and maintained code using Git.}
\end{cvitems}
}

%------------------------------------------------

\cventry
% {Grader for the Computer Engineering Department at RIT} % Job title
{Computer Engineering Department at RIT} % Organization
{Grader for Digital Systems Design II} % Job title
% {Grading for Digital Systems Design II} % Organization
{Aug. 2018 - Dec. 2018} % Date(s)
{Rochester, New York} % Location
{ % Description(s) of tasks/responsibilities
\vspace{0.5mm}
\begin{cvitems}
\item {Checked, corrected and helped with homework and quizzes for the students taking the class.}
\end{cvitems}
}


%------------------------------------------------    


\cventry
% {Undergraduate Research Assistant at RIT} % Job title
{Mechanical Engineering Department at RIT} % Organization
{Undergraduate Research Assistant} % Job title
% {Analyzing Audio Signals for Machining Monitoring with Support Vector Machine} % Organization
{May 2017 - Aug. 2018} % Date(s)
{Rochester, New York} % Location
{ % Description(s) of tasks/responsibilities
\vspace{0.5mm}
\begin{cvitems}
% \item {Developed a 50\% faster and more accurate real-time monitoring system with a partner which takes sounds produced by different machining processes and labels them according to a classifier created by a support vector machine algorithm.}
\item {Developed a 50\% faster and more accurate real-time monitoring system with a partner which analyzes sounds produced by different machining processes and labels them according to a classifier created by a support vector machine algorithm.}
\end{cvitems}
}

\end{cventries}