%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Projects}
\begin{cvvols}
{\paragraphstyle \justify
\begin{itemize}[leftmargin=2ex]
% \item Exceeded professor's expectations by adding a login system and game observation features in a 5-person team to develop a checkers-game website respecting Agile methodology using Spark with Java, HTML, and JavaScript.
\item A network-attached storage system using \textbf{Python} with a hard drive and a \textbf{Raspberry Pi} that backs up all files in real time in Google Drive.
\vspace{-1mm}
\item An application in \textbf{Python} that uses \textbf{Google Cloud Vision} and Edamam \textbf{REST API}s to provide recipes from pictures of ingredients. The user can browse and filter results based on calories and nutrient ranges.
\vspace{-1mm}
\item A command-line dictionary using \textbf{Shell} and WordsAPI \textbf{REST API} that can fetch the definition, part of speech, synonyms, antonyms, and an example of one word or multiple words.
\vspace{-1mm}
% \item Programmed a game in mixed C and ARM Assembly Language with user interaction and rules on a FRDM-KL46Z board.
\item An alarm clock system using \textbf{Python} and a \textbf{Raspberry Pi} that shows a fun fact about the day when the alarm rings. The alarm is a random track from a provided YouTube playlist link or a YouTube video link.
\vspace{-1mm}
\item An \textbf{Augmented Reality Android app} for this resume using \textbf{Unity, Vuforia, and C\#} scripts. Upon scanning the QR code in this resume with the app, it will overlay the album art and snippets of audio for all the tracks that I have composed.
\vspace{-1mm}
\item An \textbf{Android app} in \textbf{Kotlin and Java} that tracks scans from a barcode scanner. Within the app, a QR code is scanned and it pairs the devices using \textbf{Bluetooth} technology.
\vspace{-1mm}
\item A frictionless, \textbf{computer vision}-based entry system for a grocery store using \textbf{Python, OpenCV, Microsoft Azure, a Raspberry Pi, and a NVIDIA Jetson Nano}.
% \vspace{-1mm}
% \item Programmed a swift AI in Java for a pathbuilding game that could compete against humans as well as other AIs.
% \vspace{-1mm}
% \item Designed a state-machine and wrote microcode with a partner to develop a fully-functioning multicycle CPU implementation by writing microcode and ROM instructions for an Accumulator Design Instruction Set Architecture.
\end{itemize}
\vspace{-1mm}
\begin{center}
\fbox{All projects have been maintained using \textbf{Git}. More on \texttt{codeabiswas.github.io}.}
\end{center}
\vspace{-1mm}
}
\end{cvvols}